Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-19 Multiresolution_framework/ltx/manuscript.tex
small edit
mini edit to M-step

where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.  $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$). Note that this is actually the smoother output which is obtained at the E-step.

@@

\section{Construction and maximization of the Lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}

>>>>

where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.  $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$). Note that $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$), is actually the smoother output which is obtained at the E-step.

@@

\section{Construction and maximization of the lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}
